---
title: '[[ by group performance #4655'
output: html_document
date: "2024-02-15"
---


```{r}
library(data.table)

set.seed(123L)
n = 500L
n_nested = 40L
dt = data.table(ordered_id = seq_len(n),
                unordered_id = sample(n),
                value = replicate(n, data.table(val1 = sample(n_nested)), simplify = FALSE))

bench::mark(
    dt[, value[[1L]], by = ordered_id]
    , dt[, value[[1L]], by = unordered_id]
    , check = FALSE
    , time_unit = "ms" 
)

## pre-regression (1.12.8)

##  expression                             min median `itr/sec` mem_alloc
##  <bch:expr>                           <dbl>  <dbl>     <dbl> <bch:byt>
##1 dt[, value[[1L]], by = ordered_id]   0.755  0.838     1131.     401KB
##2 dt[, value[[1L]], by = unordered_id] 0.796  0.892     1033.     409KB

## Post-regression (CRAN 1.13.0)

#> # A tibble: 2 x 6
#>   expression                               min  median `itr/sec` mem_alloc
#>   <bch:expr>                             <dbl>   <dbl>     <dbl> <bch:byt>
#> 1 dt[, value[[1L]], by = ordered_id]   102.    126.         8.02    53.7MB
#> 2 dt[, value[[1L]], by = unordered_id]   0.630   0.669   1261.     409.2KB
#> # ... with 1 more variable: `gc/sec` <dbl>

## after patch

##  expression                             min median `itr/sec` mem_alloc `gc/sec`
##  <bch:expr>                           <dbl>  <dbl>     <dbl> <bch:byt>    <dbl>
##1 dt[, value[[1L]], by = ordered_id]   0.634  0.691     1358.     401KB     15.0
##2 dt[, value[[1L]], by = unordered_id] 0.651  0.778     1187.     409KB     12.8
```


```{r}
library(atime)
library(ggplot2)
library(data.table)
```


```{r}

  tdir <- tempfile()
  dir.create(tdir)
  git2r::clone("https://github.com/Rdatatable/data.table", tdir)
  
```


```{r}

atime.list.4655 <- atime::atime_versions(
  pkg.path=tdir,
  pkg.edit.fun=function(old.Package, new.Package, sha, new.pkg.path){
    pkg_find_replace <- function(glob, FIND, REPLACE){
      atime::glob_find_replace(file.path(new.pkg.path, glob), FIND, REPLACE)
    }
    Package_regex <- gsub(".", "_?", old.Package, fixed=TRUE)
    Package_ <- gsub(".", "_", old.Package, fixed=TRUE)
    new.Package_ <- paste0(Package_, "_", sha)
    pkg_find_replace(
      "DESCRIPTION", 
      paste0("Package:\\s+", old.Package),
      paste("Package:", new.Package))
    pkg_find_replace(
      file.path("src","Makevars.*in"),
      Package_regex,
      new.Package_)
    pkg_find_replace(
      file.path("R", "onLoad.R"),
      Package_regex,
      new.Package_)
    pkg_find_replace(
      file.path("R", "onLoad.R"),
      sprintf('packageVersion\\("%s"\\)', old.Package),
      sprintf('packageVersion\\("%s"\\)', new.Package))
    pkg_find_replace(
      file.path("src", "init.c"),
      paste0("R_init_", Package_regex),
      paste0("R_init_", gsub("[.]", "_", new.Package_)))
    pkg_find_replace(
      "NAMESPACE",
      sprintf('useDynLib\\("?%s"?', Package_regex),
      paste0('useDynLib(', new.Package_))
  },
  N=seq(10, 500, 100),
  setup={ 
    set.seed(123)
    dt = data.table(ordered_id = seq_len(N),
                    unordered_id = sample(N),
                    value = replicate(N, data.table(val1 = sample(40)), simplify = FALSE))
  },
  
  expr=data.table:::`[.data.table`(dt, , value[[1L]], by = unordered_id),
  #"Before"="8c5042ca9aa5c6217b460fa5e8bf01003c7be358",#https://github.com/Rdatatable/data.table/commit/8c5042ca9aa5c6217b460fa5e8bf01003c7be358
  "Regression"="06c43b102f4b97ec91cb14a0c1631f771a9a0414", #https://github.com/Rdatatable/data.table/tree/06c43b102f4b97ec91cb14a0c1631f771a9a0414
  "Fixed"="a8ec94484d2cc375d8295a94bacc5353576c238a") #https://github.com/Rdatatable/data.table/commit/a8ec94484d2cc375d8295a94bacc5353576c238a
```


```{r}
plot(atime.list.4655)+
  labs(title = "
[[ by group performance #4655")

png("atime.list.4655.png")
plot(atime.list.4655)+
  labs(title = "
[[ by group performance #4655")
dev.off()

```
```


atime.list.4655 <- atime::atime_versions(
  pkg.path=tdir,
  pkg.edit.fun=function(old.Package, new.Package, sha, new.pkg.path){
    pkg_find_replace <- function(glob, FIND, REPLACE){
      atime::glob_find_replace(file.path(new.pkg.path, glob), FIND, REPLACE)
    }
    Package_regex <- gsub(".", "_?", old.Package, fixed=TRUE)
    Package_ <- gsub(".", "_", old.Package, fixed=TRUE)
    new.Package_ <- paste0(Package_, "_", sha)
    pkg_find_replace(
      "DESCRIPTION", 
      paste0("Package:\\s+", old.Package),
      paste("Package:", new.Package))
    pkg_find_replace(
      file.path("src","Makevars.*in"),
      Package_regex,
      new.Package_)
    pkg_find_replace(
      file.path("R", "onLoad.R"),
      Package_regex,
      new.Package_)
    pkg_find_replace(
      file.path("R", "onLoad.R"),
      sprintf('packageVersion\\("%s"\\)', old.Package),
      sprintf('packageVersion\\("%s"\\)', new.Package))
    pkg_find_replace(
      file.path("src", "init.c"),
      paste0("R_init_", Package_regex),
      paste0("R_init_", gsub("[.]", "_", new.Package_)))
    pkg_find_replace(
      "NAMESPACE",
      sprintf('useDynLib\\("?%s"?', Package_regex),
      paste0('useDynLib(', new.Package_))
  },
  
  N=seq(100, 500, 100),
  setup={ 
    set.seed(123)
    dt = data.table(ordered_id = seq_len(N),
                    unordered_id = sample(N),
                    value = replicate(N, data.table(val1 = sample(40)), simplify = FALSE))
  },
  
  expr=data.table:::`[.data.table`(dt, , value[[1L]], by = unordered_id),
  "Before"="dadf52892ec66fe4861278eaeef0ef8d912e90ee",
  "Regression"="f3470bce8d2097bb6b1e3a92b5e93169d97e1cad", 
  "Fixed"="93967418ee0e40370ce9d4c4b63bf599e4ef1ecd") 

https://github.com/Rdatatable/data.table/commit/f3470bce8d2097bb6b1e3a92b5e93169d97e1cad

